
Nowadays cloud infrastructures offer a plethora of distinct hardware configurations for rent and price. We argued that autoscaling systems can use this diversity to better fulfill the SLA requirements without dramatically raising the operational cost. This has special importance for enterprises where a decrease in the user base leads to a reduction in revenue, or for cloud providers where penalties paid due to SLO violations also have a revenue impact. We proposed a novel autoscaling approach for cloud applications that allocates the most appropriate hardware configuration according to the workload and customer requirements. This system benefits from cloud heterogeneity and online profiling techniques to find the suited scaling plan. In addition, a metal classification was also proposed to find the tradeoff between two factors such as the SLO fulfillment degree and infrastructure cost adapted to customer requirements. We implemented and successfully integrated our autoscaling system in a real cloud platform. In multiple clouds, we evaluated our system in a realistic scenario showing the benefits by selecting one metal configuration or another to mitigate the performance degradations caused by traffic spikes. 
In the future we plan to extend our system by supporting a wider number of hardware configurations and a more efficient dynamic load balancing mechanism. Similarly, we want to further study the financial impact of combining hardware configurations from different cloud providers.

%Nevertheless, these benefits could also be observed along the whole execution of a larger workload trace. 

%By considering factors such as SLO fulfillment degree and infrastructure cost, our system selects the scaling plan that minimizes the performance degradations even under large and temporal workload variations.

% integrating a neural network forecasting model
% support for more types of instances.


%It is necessary to highlight the impotance of autoscaling systems that exploits the heterogeneity of the cloud infrastructures when provisioning applications.

%cheapest configuration doesn't have to be efficient. Tradittional system scale out and back using small instances.



