\documentclass[10pt]{article}

\input{conpaasdoc}

\title{ConPaaS -- API documentation\htmlonly{ [\xml{a href="api.pdf"}pdf\xml{/a}]}}
\htmltitle{ConPaaS -- API documentation}
\author{Emanuele Rocca}
\date{ConPaaS-1.0.0}

\begin{document}

\maketitle

%\T\vfil
%\T\tableofcontents
%\T\vfil
%\T\newpage

\section{Introduction}
\label{intro}
ConPaaS services are composed by a manager and one or more agents: the
manager's role is to oversee the functioning of a specific service. ConPaaS
managers are responsible, among other things, for starting up and shutting down
ConPaaS agents, which in turn provide the functionality offered by a specific
service.

It is possible to create and administer ConPaaS services through an HTTP/JSON
Application Programing Interface exposed by a web service called ConPaaS
Director. 

\pagebreak 

\section{Available methods}
Let us list the ConPaaS API methods, together with a brief description of their
behavior.

\begin{verbatim}
GET /available_services

    Return a list of available service types. For example: 
    ['scalaris', 'selenium', 'hadoop', 'mysql', 'java', 'php']

POST /start/<servicetype>

    Return a dictionary with service data (manager's vmid and IP address,
    service name and ID) in case of correct service creation. False is returned
    otherwise. Only service types returned by the 'available_services' method
    described above are allowed.

POST /stop/<serviceid>

    Return a boolean value. True in case of proper service termination, false
    otherwise. <serviceid> has to be an integer representing the service id of a
    running service.

GET  /list

    List running ConPaaS services. Return data as a list of dictionaries
    (associative arrays).

GET|POST /manager

    Proxy GET/POST requests to the manager responsible for the given service id
    (the sid parameter). This method allows to call any method made available by
    managers through the director.

GET  /download/ConPaaS.tar.gz

    Used by ConPaaS services. Download a tarball with the ConPaaS source code.

POST /callback/decrementUserCredit.php
    
    Used by ConPaaS services. Decrement user credit and check if it is enough.
    Return a dictionary with the 'error' attribute set to false if the user had
    enough credit, true otherwise.
\end{verbatim}

The first four methods, namely \textbf{start}, \textbf{stop}, \textbf{list} and
\textbf{manager} are of interest for developers wishing to control a ConPaaS
installation from their programs. They all require two additional parameters:
\textbf{username} and \textbf{password}. The remaining methods are, conversely,
only used internally by ConPaaS services and they do not require any additional
parameter. 

One of the above mentioned methods is worth a particular mention: the
\textbf{manager} method can be used to access any method available on the
manager responsible for a specific service. For example, a developer might want
to use the manager method to get the logs of running service, or add and remove
agents. 
\end{document}
