

\documentclass{sig-alternate-10pt}
%\usepackage{amssymb,amsmath}
\usepackage{mathptmx}
\usepackage[ruled,vlined,linesnumbered]{algorithm2e}

\usepackage{boxedminipage}
\usepackage{morefloats}
\usepackage{caption}

% the fixme command
\newcommand{\fixme}[1]
{
  \noindent
  \begin{boxedminipage}{\linewidth}
    \textsl{{\bf FIXME: #1}}
  \end{boxedminipage}
}


\begin{document}
\pagenumbering{arabic}
\sloppy
%



%\title{Autoscaling system for minimizing SLA violation and financial cost in Cloud platforms}
\title{Autoscaling system for minimizing SLA violation in heterogeneous Cloud infrastructures}

\numberofauthors{3}
\author{
\alignauthor Hector Fernandez \titlenote{Dr. Hector Fernandez}\\
       \affaddr{VU University Amsterdam}\\
       \affaddr{Amsterdam, The Netherlands}\\
       \email{hector.fernandez@vu.nl}
% 2nd. author
\alignauthor Guillaume Pierre \titlenote{Dr. Guillaume Pierre}\\
       \affaddr{INRIA. Universit\'{e} Rennes 1 }\\
       \affaddr{Rennes, France}\\
       \email{guillaume.pierre@irisa.fr}
% 3rd. author
\alignauthor Thilo Kielmann \titlenote{Dr. Thilo Kielmann}\\
       \affaddr{VU University Amsterdam}\\
       \affaddr{Amsterdam, The Netherlands}\\
       \email{thilo.kielmann@vu.nl}
}

\maketitle
\begin{abstract}

\end{abstract}

\keywords{Cloud computing, dynamic resource provisioning, resource heterogeneity, workload forecasting, sensitivity analysis} % NOT required for Proceedings


\section{Introduction}

\input{introduction}

\section{ Problem statement}

\input{motivation}

%\section{ConPaaS overview \label{conpaas}}

%\input{conpaasOverview}

%\section{The Wikipedia application \label{wikipedia}}

%\input{wikibench_v2}


\section{Autoscaling system}

\input{scaling_sys}


\section{Experiments \label{sec:experiments}}

\input{experiments}

\section{Related works \label{sec:relatedWorks}}

\input{relatedWorks}

\section{Conclusion \label{sec:conclusion}}

\input{conclusion}

%ACKNOWLEDGMENTS are optional
\section{Acknowledgments}
This work is funded by the FP7 Programme of the European Commission in the context of the Contrail project under Gran Agreement FP7-ICT-257438.

\balancecolumns

%\bibliographystyle{plain}
%\bibliography{socc2013}

\begin{thebibliography}{10}

\bibitem{vector_autoregression_2006}
Vector autoregressive models for multivariate time series.
\newblock In {\em Modeling Financial Time Series with S-PLUS}, pages 385--429.
  Springer New York, 2006.

\bibitem{das4}
{ Advanced School for Computing and Imaging (ASCI), The Distributed ASCI
  SuperComputer 4. }.

\bibitem{ali-eldin_2012}
Ahmed Ali-Eldin, Johan Tordsson, and Erik Elmroth.
\newblock An adaptive hybrid elasticity controller for cloud infrastructures.
\newblock In {\em NOMS'12}, pages 204--212, 2012.

\bibitem{amazonEC2}
{Amazon Elastic Compute Cloud (EC2)}.

\bibitem{trafficCongestion}
Yuliy Baryshnikov, Ed~Coffman, Guillaume Pierre, Dan Rubenstein, Mark
  Squillante, and Teddy Yimwadsana.
\newblock Predictability of web-server traffic congestion.
\newblock In {\em Proceedings of the 10th International Workshop on Web Content
  Caching and Distribution}, WCW '05, pages 97--103, Washington, DC, USA, 2005.
  IEEE Computer Society.

\bibitem{bunch_2012}
Chris Bunch, Vaibhav Arora, Navraj Chohan, Chandra Krintz, Shashank Hegde, and
  Ankit Srivastava.
\newblock A pluggable autoscaling service for open cloud paas systems.
\newblock In {\em UCC'12}, pages 191--194, 2012.

\bibitem{chandra_dynamic_2003}
Abhishek Chandra, Weibo Gong, and Prashant Shenoy.
\newblock Dynamic resource allocation for shared data centers using online
  measurements.
\newblock {\em {SIGMETRICS} Perform. Eval. Rev.}, 31(1):300--301, June 2003.

\bibitem{ec2Performance}
Jiang Dejun, Guillaume Pierre, and Chi-Hung Chi.
\newblock {EC2} performance analysis for resource provisioning of
  service-oriented applications.
\newblock In {\em Proceedings of the 3rd Workshop on Non-Functional Properties
  and SLA Management in Service-Oriented Computing}, November 2009.

\bibitem{smartscale_2012}
Sourav Dutta, Sankalp Gera, Akshat Verma, and Balaji Viswanathan.
\newblock Smartscale: Automatic application scaling in enterprise clouds.
\newblock In {\em IEEE CLOUD'12}, pages 221--228, 2012.

\bibitem{wikibench}
Guido~Urdaneta Erik-Jan~van Baaren and Guillaume Pierre.
\newblock Wikibench: A distributed, wikipedia based web application benchmark.
\newblock 2009.

\bibitem{gandhi_hybrid_2012}
Anshul Gandhi, Yuan Chen, Daniel Gmach, Martin Arlitt, and Manish Marwah.
\newblock Hybrid resource provisioning for minimizing data center {SLA}
  violations and power consumption.
\newblock {\em Sustainable Computing: Informatics and Systems}, 2(2):91--104,
  June 2012.

\bibitem{ganglia}
{Ganglia. Distributed monitoring system. http://ganglia.sourceforge.net}.

\bibitem{ghanbari_exploring_2011}
Hamoun Ghanbari, Bradley Simmons, Marin Litoiu, and Gabriel Iszlai.
\newblock Exploring alternative approaches to implement an elasticity policy.
\newblock In {\em Proc.\ IEEE CLOUD}, 2011.

\bibitem{herbst_2013}
Nikolas~Roman Herbst, Nikolaus Huber, Samuel Kounev, and Erich Amrehn.
\newblock Self-adaptive workload classification and forecasting for proactive
  resource provisioning.
\newblock In {\em Proceedings of the 4th ACM/SPEC International Conference on
  Performance Engineering}, ICPE '13, pages 187--198. ACM, 2013.

\bibitem{jiangThesis}
Dejun Jiang.
\newblock {\em Performance Guarantees For Web Applications}.
\newblock Phd thesis, VU University Amsterdam, March 2012.

\bibitem{kaviani_profiling-as--service:_2011}
Nima Kaviani, Eric Wohlstadter, and Rodger Lea.
\newblock Profiling-as-a-service: adaptive scalable resource profiling for the
  cloud in the cloud.
\newblock In {\em Proceedings of the 9th international conference on
  Service-Oriented Computing}, {ICSOC'11}, pages 157--171, Berlin, Heidelberg,
  2011. Springer-Verlag.

\bibitem{exponential_smoothing2010}
Haibo Mi, Huaimin Wang, Gang Yin, Yangfan Zhou, Dianxi Shi, and Lin Yuan.
\newblock Online self-reconfiguration with performance guarantee for
  energy-efficient large-scale cloud computing data centers.
\newblock In {\em 2010 {IEEE} International Conference on Services Computing
  ({SCC)}}, pages 514--521, July.

\bibitem{muppala_regression-based_2012}
Sireesha Muppala, Xiaobo Zhou, Liqiang Zhang, and Guihai Chen.
\newblock Regression-based resource provisioning for session slowdown guarantee
  in multi-tier internet servers.
\newblock {\em Journal of Parallel and Distributed Computing}, 72(3):362--375,
  March 2012.

\bibitem{openshift}
{OpenShift. https://openshift.redhat.com/app/flex}.


\bibitem{conpaasIC}
Guillaume Pierre and Corina Stratan.
\newblock {ConPaaS}: a platform for hosting elastic cloud applications.
\newblock {\em IEEE Internet Computing}, 16(5):88--92, September-October 2012.

\bibitem{outagesTimes}
Linnie Rawlinson and Nick Hunt.
\newblock Jackson dies, almost takes internet with him.
\newblock {\em CNN}, Jun 2009.

\bibitem{right-scale}
{RightScale. http://www.rightscale.com//}.

\bibitem{rackspace}
{Rackspace. http://www.rackspace.com//}.

\bibitem{roy_efficient_2011}
N.~Roy, A.~Dubey, and A.~Gokhale.
\newblock Efficient autoscaling in the cloud using predictive models for
  workload forecasting.
\newblock In {\em 2011 {IEEE} International Conference on Cloud Computing
  ({CLOUD)}}, pages 500--507, July.

\bibitem{roy_2011}
Nilabja Roy, Abhishek Dubey, Aniruddha Gokhale, and Larry Dowdy.
\newblock A capacity planning process for performance assurance of
  component-based distributed systems.
\newblock In {\em Proceedings of the 2nd ACM/SPEC International Conference on
  Performance engineering}, ICPE '11, pages 259--270, New York, NY, USA, 2011.
  ACM.

\bibitem{sharma_cost-aware_2011}
Upendra Sharma, P.~Shenoy, S.~Sahu, and A.~Shaikh.
\newblock A cost-aware elasticity provisioning system for the cloud.
\newblock In {\em 2011 31st International Conference on Distributed Computing
  Systems ({ICDCS)}}, pages 559 --570, June 2011.

\bibitem{sotomayor_virtual_2009}
Borja Sotomayor, Ruben {S.} Montero, Ignacio {M.} Llorente, and Ian Foster.
\newblock Virtual infrastructure management in private and hybrid clouds.
\newblock {\em {IEEE} Internet Computing}, 13(5):14--22, October 2009.

\bibitem{urgaonkar_agile_2008}
Bhuvan Urgaonkar, Prashant Shenoy, Abhishek Chandra, Pawan Goyal, and Timothy
  Wood.
\newblock Agile dynamic provisioning of multi-tier internet applications.
\newblock {\em {ACM} Trans. Auton. Adapt. Syst.}, 3(1):1--39, March 2008.

\bibitem{dejavu2012}
Nedeljko Vasić, Dejan Novaković, Svetozar Miu{\textbackslash}vcin, Dejan
  Kostić, and Ricardo Bianchini.
\newblock {DejaVu:} accelerating resource allocation in virtualized
  environments.
\newblock {\em {SIGARCH} Comput. Archit. News}, 40(1):423--436, March 2012.

\bibitem{mediawiki}
{Wikipedia Foundation}.
\newblock MediaWiki a free software wiki package. {http://www.mediawiki.org}.

\bibitem{azure-project}
{WindowsAzure. http://www.windowsazure.com/}.

\bibitem{wolski_network_1999}
Rich Wolski, Neil~T. Spring, and Jim Hayes.
\newblock The network weather service: A distributed resource performance
  forecasting service for metacomputing.
\newblock {\em Journal of Future Generation Computing Systems}, 15:757--768,
  1999.

\end{thebibliography}



\end{document}
